\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-12 paper/paper.tex
Begin computation subsection, add references

\subsection{Computation}
Discuss the MCMC approach, RStan, etc.

>>>>

\subsection{Computation}
Each model was fit in {\t R} \nocite{r} using Hamiltonian Monte Carlo
\cite{betancourt} as implemented in {\tt
  rstan}\cite{rstan}. Multiple chain were run with _000 iterations of
warmup. Convergence was assessed by examining posterior
plots and checking that Gelman-Rubin diagnostics were close to 1.
